\textit{Urban and building multiscale co-simulation: case study implementations on two university campuses}

### 2016-11-28 latex/UMEM_CoSim.tex
Content Updates

\section{Introduction}\noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}

@@

As of version 8.1.0, EnergyPlus supports exporting a simulation model as a
Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}. This
feature introduces new IDF objects to specify the interface such an FMU
exposes. These objects define which output variables are exported by the FMU
and which variables are imported. The FMU export functionality is closely
linked to the Energy Management System (EMS) of EnergyPlus. Co-simulation
exchange variables either mimic an EnergyPlus schedule, an EMS variable or
drive an EMS actuator. Since the model used by CitySim to simulate a building
is more abstract than the model used by EnergyPlus, the EMS is used to
aggregate certain values. CitySim does not model windows separately. Therefore,
a weighted average of window and wall surface temperatures is calculated with
EMS subroutines.\noteDT{@JK: is this last statement correct?}

@@

\subsection{EnergyPlus co-simulation results}
After calibration, a comparison of co-simulation and solo EnergyPlus
simulations is made. For cooling, a discrepancy can be seen between co-
simulation and solo EnergyPlus. Co-simulation results in a 20.2\% decrease in
predicted cooling energy, as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 4.8\% due to co-simulation. The exchange of long wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.
These performance differences due to co-simulation are compared to a
theoretical single-zone case study in which there was a 15-30\% increase in
heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
The results from this scenario are less extreme on the heating side and more
on the cooling side than the theoretical case study.

@@

With a particularly strong visual and formal identity, the SwissTech
Convention Centre (STCC) is clearly the key protagonist.\noteDT{move main
sentence to start of paragraph} Applied with essential functions for the
region, the building has definitely become the new landmark. Designed as a
Minergie\noteDT{ref?} building, it includes modern energy conversion
technologies to reduce its energy consumption. The focus of the co-simulation
is realized on the STCC, simulated with the nearby buildings for housing,
retail and service areas.

\subsection{Model development}
The information required in the simulation mainly comprises three parts:
physical, geometrical and operational data. The geometry information including
the shape, dimension, structure and materials was obtained from the Real
Estate and Infrastructure Department of École Polytechnique Fédérale de
Lausanne (EPFL), which was responsible for carrying out the project from call
to tender to construction. However, since the documents provided were full of
details but also conflicting with what has been installed as compared to the
documents before construction, the task to realize a precise model of the
buildings itself is rather tedious. Besides, it is even more challenging to
get the operational data (daily occupancy, lighting, and electrical equipment
usage level and ventilation rate) as the building has only recently been set
in operation mode and as engineers and technicians have been working on
improving the controls. Therefore, due to unreliable monitoring data, the
calibration step of the model has been unfortunately\noteDT{delete:
"unfortunately". we are cold hard scientists battling the evil nemesis that is
entropy and his plan to suffocate everyone with the inevitable heat death of
the universe. we have no time for lame excuses. we just abandon. no regrets.
thug life!} abandoned.\\

@@

\subsection{EnergyPlus co-simulation results}
The Quartier Nord building is also simulated within the solo and
cosimulation environments. When
focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
that the HPI and theoretical case studies due to the number and proximity of
surrounding buildings is not as large. \noteCM{I'm planning to elaborate on
these sections
but am struggling to interpret the results other than just "co-sim and solo
are different" -- what do you guys think?}\noteDT{well, for a start, the two
case studies differ in the amount of LWR radiation. we could quantify that?
also, the number of surfaces of the e+ model with viewfactor to surrounding
buildings?}

@@

\subsection{CitySim co-simulation results}

When focusing solely on CitySim, a 26.9\% decrease in heating energy is
observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
decrease in heating energy is observed, as seen in Figure
\ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
previous comparison of EnergyPlus and CitySim engines. The substantial
differences between solo and co-simulation in these cases is a result of
EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
interpreting these results -- you mentioned that there is an expected delta
between citysim and energyplus in previous studies. Can you help elaborate on
that?}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
\label{fig:qn_citysim_cosimvssolo_cooling}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
\caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
\label{fig:qn_citysim_cosimvssolo_heating}
\end{figure}

@@

\subsection{Acknowledgements}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project. The authors would also like to acknowledge
 Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}

>>>>

\section{Introduction}
% \noteCM{Clayton's notes are red!}\noteJK{Jerome's notes are blue!}\noteDT{Daren's notes are green!}

@@

As of version 8.1.0, EnergyPlus supports exporting a simulation model as a
Functional Mock-up Unit (FMU) \citep{Nouidui:2014hq,Anonymous:ZZTfF80-}. This
feature introduces new IDF objects to specify the interface such an FMU
exposes. These objects define which output variables are exported by the FMU
and which variables are imported. The FMU export functionality is closely
linked to the Energy Management System (EMS) of EnergyPlus. Co-simulation
exchange variables either mimic an EnergyPlus schedule, an EMS variable or
drive an EMS actuator. Since the model used by CitySim to simulate a building
is more abstract than the model used by EnergyPlus, the EMS is used to
aggregate certain values. CitySim does not model windows separately. Therefore,
a weighted average of window and wall surface temperatures is calculated with
EMS subroutines.
% \noteDT{@JK: is this last statement correct?}

@@

\subsection{EnergyPlus co-simulation results}
After calibration, a comparison of co-simulation and solo EnergyPlus
simulations is made. For cooling, a discrepancy can be seen between co-
simulation and solo EnergyPlus. Co-simulation results in a 15.5\% decrease in
predicted cooling energy, as seen in Figure
\ref{fig:hpi_energypluscooling}. Figure \ref{fig:hpi_energyplusheating}
illustrates the difference in predicted heating energy consumption across the
test year. A consistent offset exists across the time frame of days in
January, the peak of the heating season. A more varied discrepancy across the
heating months is noticed resulting an overall increase of heating prediction
of 6.5\% due to co-simulation. The exchange of long wave radiation for this
particular site is substantial due to the proximity of surrounding buildings.
These performance differences due to co-simulation are compared to a
theoretical single-zone case study in which there was a 15-30\% increase in
heating energy and a 4-11\% decrease in cooling energy \citep{Miller:2015vk}.
The results from this scenario are less extreme on the heating side and more
on the cooling side than the theoretical case study.

When comparing the solo and co-simulated models to the measured data, it is noticed that 
cooling energy is over-predicted by the solo simulation by 4\%, while co-simulation under-predicted 
by 11.1\%. For heating energy, co-simulation was able to bring the predicted value to within 2\% of 
the measured value for the year, an improvement as compared to the solo simulation, which was 8.5\% less than the measured value.

@@

With a particularly strong visual and formal identity, the SwissTech
Convention Centre (STCC) is clearly the key protagonist. Applied with essential functions for the
region, the building has definitely become the new landmark. Designed as a
Minergie building, it includes modern energy conversion
technologies to reduce its energy consumption. The focus of the co-simulation
is realized on the STCC, simulated with the nearby buildings for housing,
retail and service areas.
% \noteDT{move main
% sentence to start of paragraph}

\subsection{Model development}
The information required in the simulation mainly comprises three parts:
physical, geometrical and operational data. The geometry information including
the shape, dimension, structure and materials was obtained from the Real
Estate and Infrastructure Department of École Polytechnique Fédérale de
Lausanne (EPFL), which was responsible for carrying out the project from call
to tender to construction. However, since the documents provided were full of
details but also conflicting with what has been installed as compared to the
documents before construction, the task to realize a precise model of the
buildings itself is rather tedious. Besides, it is even more challenging to
get the operational data (daily occupancy, lighting, and electrical equipment
usage level and ventilation rate) as the building has only recently been set
in operation mode and as engineers and technicians have been working on
improving the controls. Therefore, due to unreliable monitoring data, the
calibration step of the model was not undertaken.\\
% \noteDT{delete:
% "unfortunately". we are cold hard scientists battling the evil nemesis that is
% entropy and his plan to suffocate everyone with the inevitable heat death of
% the universe. we have no time for lame excuses. we just abandon. no regrets.
% thug life!}

@@

\subsection{EnergyPlus co-simulation results}
The Quartier Nord building is also simulated within the solo and
cosimulation environments. When
focusing on the EnergyPlus results, a 7.5\% decrease in cooling energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_cooling}. A 2.8\% increase in heating energy is
observed, as seen in Figure
\ref{fig:qn_eplus_cosimvssolo_heating}. These differences are less pronounced
that the HPI and theoretical case studies due to the number and proximity of
surrounding buildings is not as large. Long wave radiation exchange in this situation 
doesn't have as large of an impact on the heating and cooling calculations.
% \noteCM{I'm planning to elaborate on
% these sections
% but am struggling to interpret the results other than just "co-sim and solo
% are different" -- what do you guys think?}\noteDT{well, for a start, the two
% case studies differ in the amount of LWR radiation. we could quantify that?
% also, the number of surfaces of the e+ model with viewfactor to surrounding
% buildings?}

@@

% \subsection{CitySim co-simulation results}

% When focusing solely on CitySim, a 26.9\% decrease in heating energy is
% observed, as seen in Figure \ref{fig:qn_citysim_cosimvssolo_cooling}. A 49.1\%
% decrease in heating energy is observed, as seen in Figure
% \ref{fig:qn_citysim_cosimvssolo_heating}. These results align with the
% previous comparison of EnergyPlus and CitySim engines. The substantial
% differences between solo and co-simulation in these cases is a result of
% EnergyPlus transferring the heating and cooling load values at each time step. \noteCM{Jerome -- I need some help
% interpreting these results -- you mentioned that there is an expected delta
% between citysim and energyplus in previous studies. Can you help elaborate on
% that?}

% \begin{figure}[H]
% \centering
% \includegraphics[scale=0.55]{figures/QN_CitySim_Cooling}
% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Cooling}
% \label{fig:qn_citysim_cosimvssolo_cooling}
% \end{figure}

% \begin{figure}[H]
% \centering
% \includegraphics[scale=0.55]{figures/QN_CitySim_Heating}
% \caption{Quartier Nord CitySim Co-Simulation vs. Solo for Heating}
% \label{fig:qn_citysim_cosimvssolo_heating}
% \end{figure}

@@

\subsection{Acknowledgements}
The authors would like to acknowledge the ETH Z\"urich Campus Facilities
Department, the EPFL Real Estate and Infrastructure Department, and Emanuel
Thoma for their assistance in this project. This research was funded by the
Competence Center in Energy and Mobility (CCEM) under the Urban Multi-scale
Energy Modeling (UMEM) project. 
% The authors would also like to acknowledge
 % Emanuel Thoma for his work in developing the geometric models.% %
 % \noteDT{We also
% want to acknowledge Emanuel Thoma for his work on the Hoenggerberg model, no?}
